---
title: "Exploratory Machine"
subtitle: "Data Product project"
author: "Bruno Berrehuel"
github: "www.github.com"
date: "January 28, 2017"
output: ioslides_presentation 
#output: beamer_presentation # can do beamer slides too
# compile with ùkr
---

<style>
#title {
    background-color:hsl(280,100%,75%);
    color:black;
    padding-right:187px;
    padding-left:10px;
    margin-left:-10px;
}
#subtitle {
    background-color:hsl(280,50%,75%);
    color:black;
    padding-right:187px;
    padding-left:10px;
    margin-left:-10px;
}
</style>

## Exploratory Machine | hands on

## Side Panel

## Scatterplot tab

## Distribution tab

## Summary and Structure tab

Some content very interesting

## cheatsheet

### outstanding subtitle

#### subsubtitle

Some content.

- item a
- item b

1. bullet 1
1. bullet 2

Plain text

*italicized*

**bold text**

`code : for (i %in% 1:10) {
print(i+10)
}`

## R code chunk - compiled

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA) # default setting
```

```{r}
head(mtcars)
```

## plot with R

```{r plot, fig.align="center", fig.cap="Awesome figure"}
plot(mtcars$wt, mtcars$mpg, xlab="weight", ylab="miles per gallon")
# can add echo=FALSE to have just plot
# all knitr options are available
```
